---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

Data data is provided inside the [activity.zip](activity.zip) file.

Note: To extract the contents in Mac OS you my use `$ unzip activity.zip`.

The document is reasonably well formatted, as such, we may loaded it with the appropriate classes before hand:

```{r}
rawData <- read.csv("activity.csv", colClasses = c("numeric", "Date", "numeric"))
```

## What is mean total number of steps taken per day?

The total number of days may be determined as such:

```{r}
stepsSum <- aggregate(steps ~ date, rawData, sum)
```

```{r, echo=FALSE}
barplot(height = stepsSum$steps, width = as.numeric(stepsSum$date), xlab = "Days", ylab = "Total steps", main = "Total steps over time")
```

Although we use `barplot` to plot the graphic `Total steps over time`, this graph is a histogram over the days the data refers to.

Lets also look at the `mean` and `median`:

```{r}
stepsMean <- aggregate(steps ~ date, rawData, mean)
```

```{r, echo=FALSE}
barplot(height = stepsMean$steps, width = as.numeric(stepsMean$date), xlab = "Days", ylab = "Mean steps", main = "Mean steps over time")
```

```{r}
stepsMedian <- aggregate(steps ~ date, rawData, median)
```
```{r, echo=FALSE}
barplot(height = stepsMedian$steps, width = as.numeric(stepsMedian$date), xlab = "Days", ylab = "Median steps", main = "Median steps over time")
```

We notice that the `median` of the number of steps taken is `0`, which looks rather odd.

## What is the average daily activity pattern?

The interval frequencies mean is the following:

```{r}
stepsIntervals <- aggregate(steps ~ interval, rawData, mean)
```

Visualizing this data as a timeseries we get:

```{r, echo=FALSE}
barplot(height = stepsIntervals$steps, width = stepsIntervals$interval, xlab = "Interval", ylab = "Mean steps")
```

Which allows us to also determine the interval of the day with the maximum number of steps on average:

```{r}
stepsIntervals[stepsIntervals$steps == max(stepsIntervals$steps),]$interval
```

## Imputing missing values

The observed results are using unknown data underneath. To assess the number of entries missing data may be determined as such:

```{r}
length(rawData[is.na(rawData$steps),]$steps)
```

To fill in the gaps we'll use the mean per interval of the known values.

## Are there differences in activity patterns between weekdays and weekends?
